---
title: "Draft Quarto document"
author: "Your Name"
format: html
---

## Header 1
Setup i chincs fortæller at denne køres hver gang

```{r setup}
library(tidyverse)
library(here)
source(here("R/functions.R"))
library(fs)
```


## Importing new data

```{r}
#| eval: false
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )
```


## Create my first function and documentation of it

```{r}
#| eval: false
#' Add two numbers together.
#'
#' @param num1 A number here.
#' @param num2 A number here.
#'
#' @returns Returns the sum of two numbers
#'
add_numbers <- function(num1, num2) {
  added <- num1 + num2
  return(added)
}
```


```{r}
#| eval: false
#| output: false #bliver ikke printet i html
#|
#' Read in one nurses' stress data file.
#'
#' @param file_path A path to a datafile
#'
#' @returns outputs a dataframe/ tibble

read <- function(file_path) {
  data <- file_path |>
    read_csv(
      show_col_types = FALSE,
      name_repair = to_snake_case,
      n_max = 100
    )
  return(data)
}
```


```{r}
#| eval: false

# Outputs only 100 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read()

# Outputs only 1000 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = 1000)

# Outputs all rows (`Inf` means infinity)
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = Inf)
```

##Using map 
```{r}
hr_files <- here("data-raw/nurses-stress/") %>%
  dir_ls(regexp = "HR.csv.gz", recurse = TRUE) # dir_ls giver liste af filer inden for folder. Recurse giver adgang til alle foldere inden for angivne folder

hr_files

hr_data <- hr_files %>%
  map(read) %>% # OBS no brackets
  list_rbind(names_to = "file_path_id")
```


##Exercise: Convert map to function and use on sleep
```{r}
#| eval: false

#' Read in all files at once
#'
#' @param filename
#'
#' @returns outputs a dataframe

read_all <- function(filename) {
  files <- here::here("data-raw/nurses-stress/") %>%
    fs::dir_ls(regexp = filename, recurse = TRUE)

  data <- files %>%
    purrr::map(read) %>%
    purrr::list_rbind(names_to = "file_path_id")
  return(data)
}

read_all("HR.csv.gz")
```


## Inspecting the data
```{r}
#| eval: false
hr_data <- read_all("HR.csv.gz")

survey_data <- here("data-raw/nurses-stress/survey-results.csv.gz") |>
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case
  )

hr_data
survey_data
```

## Extract ID
```{r}
hr_data %>%
  mutate(
    id = str_extract(
      file_path_id,
      pattern = "/stress/[:alnum:]{2}/"
    ) %>%
      str_remove("/stress/") %>% str_remove("/"),
    .before = file_path_id
  ) %>%
  select(-file_path_id)
```


##Convert get-ID-code to a function
```{r}
#' Get ID code from file_path_id
#'
#' @param data
#'
#' @returns outputs a dataframe

get_participant_id <- function(data) {
  data <- data %>%
    dplyr::mutate(
      id = stringr::str_extract(
        file_path_id,
        pattern = "/stress/[:alnum:]{2}/"
      ) %>%
        stringr::str_remove("/stress/") %>% str_remove("/"),
      .before = file_path_id
    ) %>%
    dplyr::select(-file_path_id)
  return(data)
}

get_participant_id(hr_data)
```

## Working with across
```{r}
hr_data <- read_all("HR.csv.gz") %>%
  get_participant_id()

hr_data
```

```{r}
hr_data %>%
  summarise(across(where(is.numeric), list(
    mean = mean,
    median = median,
    sd = sd
  )))
```

## Working with dates
```{r}
hr_data %>%
  mutate(
    datetime = round_date(collection_datetime,
      unit = "minute"
    ),
    .before = "collection_datetime"
  )
```

## Summarising by groups
```{r}
hr_data %>%
  mutate(collection_datetime = round_date(collection_datetime,
    unit = "minute"
  )) %>%
  summarise(
    across(where(is.numeric), list(mean = mean, sd = sd, median = median)),
    .by = c(id, collection_datetime)
  )
```


## 
```{r}
#' Function to calculate summary statistics for collumns
#'
#' @param data
#'
#' @returns a datatable

summarise_by_datetime <- function(data) {
  summarised_data <- data %>%
    dplyr::mutate(collection_datetime = lubridate::round_date(collection_datetime,
      unit = "minute"
    )) %>%
    dplyr::summarise(
      across(tidyselect::where(is.numeric), list(mean = mean, sd = sd, median = median)),
      .by = c(id, collection_datetime)
    )
  return(summarised_data)
}

summarise_by_datetime(hr_data)
```


## Pivot longer

```{r}
survey_data <- here("data-raw/nurses-stress/survey-results.csv.gz") %>%
  read()

survey_data
```


```{r}
survey_tidy <- survey_data %>%
  mutate(
    date = mdy(date),
    start_datetime = as_datetime(paste(date, start_time)),
    end_datetime = as_datetime(paste(date, end_time)),
    datetime_id = start_datetime,
    .before = start_time
  ) %>%
  select(-c(date, start_time, end_time, duration))
```


```{r}
survey_tidy %>%
  select(id, , datetime_id, start_datetime, end_datetime) %>%
  pivot_longer(c(start_datetime, end_datetime), names_to = NULL, values_to = "collection_datetime") %>%
  group_by(pick(-collection_datetime)) %>%
  complete(collection_datetime = seq(min(collection_datetime),
    max(collection_datetime),
    by = 60
  )) %>%
  ungroup()
```


## Create a function on survey_tidy + survey_long
```{r}
#' Tidy up the dates in the survey results
#'
#' @param dataframe of the survey results data
#'
#' @returns. A data frame

tidy_survey_dates <- function(data) {
  tidied <- data %>%
    dplyr::mutate(
      date = mdy(date),
      start_datetime = lubridate::as_datetime(paste(date, start_time)),
      end_datetime = lubridate::as_datetime(paste(date, end_time)),
      datetime_id = start_datetime,
      .before = start_time
    ) %>%
    dplyr::select(-c(date, start_time, end_time, duration))
  return(tidied)
}


```
